---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(magick)
library(tidyverse)
logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSvn_sGjpX_AnZapFj6fkaQjEy4WgN-Szxi4BCG5fxnlUFOCz_pRx9LPGfc0VomjzIcp5R599-uUh3G/pub?output=csv") %>%
    rename(PlayerSpecies = 2, OpponentSpecies = 3, 'rank' = 4, Upgrade_Advantage = 5, Time_of_first_attack = 6, Time_of_game_ending = 7, Match_Winner = 8) 
logged_data$Matchup <- paste(logged_data$PlayerSpecies, logged_data$OpponentSpecies)

```

```{css}
h2{

}
p{

}
```



## Tracking How Different Parameters Can Affect The Duration and Result of a Starcraft 2 Game.

When watching pro-level Starcraft 2, the upgrade advantage was something often emphasized. As an admittedly much less competent player than some of the best in the world, I was curious if there would be any affect it would make on my gameplay results.

```{r, fig.align='center'}
## generate graph
ggplot(data = logged_data) +
  geom_bar(aes(x = Upgrade_Advantage,
               fill = Match_Winner)) + ## should show the proportion of win rate to upgrade advantage (if one column is coloured exclusively one way or the other, it will show signs of correlation)
  ## Front end polish.
  labs(title = "Win Rate Based On Upgrade Advantage",
       x = "upgrade advantage",
       y = "Number of Games",
  )
## generate win rate.
win_rate <- round(length(logged_data$Match_Winner[logged_data$Match_Winner == "Player"]) / nrow(logged_data), 2)
```

Looking at this data, it's very clear that the upgrades played a very small if any role in determining the victor: Each bar seems to show the opponent having a slight advantage in wins, which simply correlates to my win rate during the observations, which totaled to `r win_rate * 100`%.



In Starcraft 2, games can often snowball from the result of the first fight: the player who wins the first fight can often have an advantage in winning the next, and so on until they win the game. To see if the matchup played affects this, we'll look at the difference in time between the first fight and the game ending, and compare each matchup, to see if any particular matchup stands out as incredibly volatile or stagnant.

```{r, fig.align='center'}
ggplot(data = logged_data) +
  geom_bar(aes(x = Time_of_game_ending - Time_of_first_attack, ##if this number is large, it means that the first fight is less meaningful. 
               fill = Matchup)) + 
  
  ## Front end polish.
  labs(title = "Snowball Effect of the First Encounter Based on Matchup",
       x = "Time between the first attack and the game ending",
       y = "Number of Games",
  )


```

Looking at this data, we can immediately see a problem; there are too many categories for the amount of data. For this specific inquiry as well, fields like "Protoss Terran" and "Terran Protoss" are redundant distinctions. Interestingly, one version of the matchup is actually missing: "Terran Protoss", as I suppose by pure chance I did not run into that matchup in my findings. Given this, more data will likely have to be collected in order to draw sufficient conlusions. Still, looking at the graph we can see a few eye-catching things: while there seems to be a pretty standard bell curve forming between 0 and 5 minutes indicating no correlation, we are also seeing some interesting outliers: all three of the zerg matchups seem to rest by 9 exactly minutes, and terran zerg seems to have the least stable trend, being the graph's sole minimum time and maximum time difference.


